Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-10 paper.tex
Citations for ELIZA.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
\documentclass{acm_proc_article-sp}

@@

\subsection{Extensible dialog with AIML}
The child can interact with the Princess, and other agents within
Nell, directly.  Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult.  We leverage
the AIML language developed for AliceBot~\cite{alicebotxxx}, which has
won several Turing contests. \textbf{XXX more precise here XXX}
\footnote{Anecdotal evidence shows that interactions with Eliza-style
  responders can be rewarding: one woman spent hours each day
  conversing with the original Eliza.~\cite{RadioLab}}

% eliza interactions, show fragment
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.  Figure~\ref{fig:aiml}
illustrates how this can be used to implement a traditional
text adventure interaction for a particular story module.
The child can write instructions such as, ``go north'', ``go
east'', or ``open door'' for the agent.  These cause trigger events
which the activity responds to to move the agent through the
adventure---for example, by drawing the new location and causing
the agent to describe it.

>>>>

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
\documentclass{acm_proc_article-sp}
\usepackage{url}

@@

\subsection{Extensible dialog with AIML}
The child can interact with the Princess, and other agents within
Nell, directly.  Convincing discourse is a hard problem, but
reasonable approximations do not have to be difficult; even
the rudimentary conversational abilities of ELIZA elicited hours of
conversation~\cite{weizenbaum:power}.
% her secretary is divulging her life story
% asks him to leave the room so he could be alone with it
% hours discussing her boyfriend.
Nell's use as an interactive diary is enhanced by the child's
collaboration in the fiction that Nell is intelligent---what
Turkle~\cite{turkle:alone} calls the ``ELIZA effect.''

\footnote{Wilcox identifies several shortcomings with the expressive
  power of AIML, proposing ChatScript as a
  replacement~\cite{wilcox:2010}.  At present AIML's community and
  diversity of third-party implementations make it preferable.}

  We leverage
the AIML language developed for AliceBot~\cite{alicebotxxx}, which has
won several Turing contests. \textbf{XXX more precise here XXX}

% show fragment
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.  Figure~\ref{fig:aiml}
illustrates how this can be used to implement a traditional
text adventure interaction for a particular story module.
The child can write instructions such as, ``go north'', ``go
east'', or ``open door'' for the agent.  These cause trigger events
which the activity responds to to move the agent through the
adventure---for example, by drawing the new location on the page and causing
the agent to describe it.
